Tutorial_2a

### 2024-10-18 Tutorial_2a.Rmd
update tutorial 2a

# Load the person-trial-bin data set that we saved in Tutorial 1.

@@

model_M4 <- 
   brm(data = M4_data,
       family = binomial(link="cloglog"),
       event | trials(1) ~ 0 + Intercept + # Note that duplicate terms in the model formula are ignored
                          condition*period_9*trial_c + 
                          condition*period_9*I(trial_c^2) + 
                          condition*I(period_9^2)*trial_c +
                          condition*I(period_9^2)*I(trial_c^2) +
                          condition*I(period_9^3) +
                          trial_c*I(period_9^3) +
                          (1 +  condition*period_9*trial_c +
                                condition*period_9*I(trial_c^2) + 
                                condition*I(period_9^2)*trial_c +
                                condition*I(period_9^2)*I(trial_c^2)  
                                condition*I(period_9^3) +
                                trial_c*I(period_9^3) | pid),
       prior = priors_M4,
       chains = 4, cores = 4, iter = 3000, warmup = 1000,
       control = list(adapt_delta = 0.999, step_size = 0.04, max_treedepth = 12),
       seed = 12, init = "0",
       file = "Tutorial_2_Bayesian/models/model_M4")
```

>>>>

# Load the person-trial-bin data set that we saved in Tutorial 1a.

@@

model_M4 <- 
   brm(data = M4_data,
       family = binomial(link="cloglog"),
       event | trials(1) ~ 0 + Intercept + # Note that duplicate terms in the model formula are ignored
                          condition*period_9*trial_c + 
                          condition*period_9*I(trial_c^2) + 
                          condition*I(period_9^2)*trial_c +
                          condition*I(period_9^2)*I(trial_c^2) +
                          condition*I(period_9^3) +
                          trial_c*I(period_9^3) +
                          (1 +  condition*period_9*trial_c +
                                condition*period_9*I(trial_c^2) + 
                                condition*I(period_9^2)*trial_c +
                                condition*I(period_9^2)*I(trial_c^2)  +
                                condition*I(period_9^3) +
                                trial_c*I(period_9^3) | pid),
       prior = priors_M4,
       chains = 4, cores = 4, iter = 3000, warmup = 1000,
       control = list(adapt_delta = 0.999, step_size = 0.04, max_treedepth = 12),
       seed = 12, init = "0",
       file = "Tutorial_2_Bayesian/models/model_M4")
```
